Software Citation Principles

### 2016-03-22 sc-principles/software-citation-principles.tex
removing "commercial" when describing software that may no longer be available

The Accessibility principle (\ref{principle:accessibility}) states that ``software citations should permit and facilitate access to the software itself.''
This does not mean that the software must be freely available.
Rather, the metadata should provide enough information that the software can be accessed.
If the software is free, the metadata will likely provide an identifier that can be resolved to a URL that contains the specific version of the software that is being cited.
For commercial software, the metadata should still provide information on how to access the specific software, but this may be a link to a web site that allows the software be purchased or a company's product number.
As stated in the Persistence principle (\ref{principle:persistence}), we recognize that the commercial software version may no longer be available, but it still should be cited along with information about how it was accessed.

>>>>

The Accessibility principle (\ref{principle:accessibility}) states that ``software citations should permit and facilitate access to the software itself.''
This does not mean that the software must be freely available.
Rather, the metadata should provide enough information that the software can be accessed.
If the software is free, the metadata will likely provide an identifier that can be resolved to a URL that contains the specific version of the software that is being cited.
For commercial software, the metadata should still provide information on how to access the specific software, but this may be a link to a web site that allows the software be purchased or a company's product number.
As stated in the Persistence principle (\ref{principle:persistence}), we recognize that the software version may no longer be available, but it still should be cited along with information about how it was accessed.
